Abstract

### 2024-09-16 output/Main_text.Rmd
Update table footers to approximate APA 7 style
Update position of tables in text
Tables need to be re-positioned to be in a single page, avoiding long blanks before
Put "keywords" title in italics as per APA style

**Keywords:** Multidimensional IRT, 2-Parameter Logistic model,
multidimensional item discrimination, multidimensional item difficulty,
item vector representation, test space

@@

The sample items have the same `r MODEL_ACRONYM` parameters
in both latent spaces.
However, their multidimensional parameters differ due to the correlation among
the latent dimensions.
The parameters in both spaces,
along with their corresponding `r MODEL_ACRONYM` parameters,
are shown in Table \@ref(tab:example-items-table-out).

>>>>

*Keywords:* Multidimensional IRT, 2-Parameter Logistic model,
multidimensional item discrimination, multidimensional item difficulty,
item vector representation, test space

@@

The sample items have the same `r MODEL_ACRONYM` parameters
in both test spaces.
However, their multidimensional parameters differ due to the correlation among
the latent dimensions.
The parameters in both spaces,
along with their corresponding `r MODEL_ACRONYM` parameters,
are shown in Table \@ref(tab:example-items-table-out).
